### 2014-03-01 src/paper.Rnw
update

\subsection{Occurrence of Operators}
\begin{figure*}[t]
<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
o.all <- cbind(projects = rownames(o.pit.all), stack(o.pit.all))
o.all$ind <- clean(o.all$ind)
bcol <- '#2171B5'
#bcol <- 'darkgray'
icol <- '#9ECAE0'
#icol <- 'lightgray'
with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.5)))
o.det <- cbind(projects = rownames(o.pit.det), stack(o.pit.det))
o.det$ind <- clean(o.det$ind)
with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, add=T,pch='.', axes=F, ylim=c(0,0.5)))

r.all <- cbind(projects = rownames(r.pit.all), stack(r.pit.all))
r.all$ind <- clean(r.all$ind)
with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.5)))
r.det <- cbind(projects = rownames(r.pit.det), stack(r.pit.det))
r.det$ind <- clean(r.det$ind)
with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, add=T,pch='.', axes=F,ylim=c(0,0.5)))
@
\caption{Relative fertility of mutation operators. The gray boxes represent detected mutants, while black represents total mutants.}
\label{fig:mfert}

>>>>

\subsection{Occurrence of Operators}
\begin{figure*}[t]
<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
o.all <- cbind(projects = rownames(o.pit.all), stack(o.pit.all))
o.all$ind <- clean(o.all$ind)
bcol <- '#2171B5'
#bcol <- 'darkgray'
icol <- '#9ECAE0'
#icol <- 'lightgray'
o.det <- cbind(projects = rownames(o.pit.det), stack(o.pit.det))
o.det$ind <- clean(o.det$ind)
with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F, ylim=c(0,0.5)))
with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.5),add=T))

r.all <- cbind(projects = rownames(r.pit.all), stack(r.pit.all))
r.all$ind <- clean(r.all$ind)
r.det <- cbind(projects = rownames(r.pit.det), stack(r.pit.det))
r.det$ind <- clean(r.det$ind)
with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F,ylim=c(0,0.5)))
with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.5),add=T))
@
\caption{Relative fertility of mutation operators. The gray boxes represent detected mutants, while black represents total mutants.}
\label{fig:mfert}
